\section{Issue of shares}

\subsection{Directors to issue shares}

\begin{enumerate}[label=(\alph*)]
    \item Without prejudice to any special rights previously conferred on the holders of any existing shares or class of shares and subject to the Act and the Shareholders Agreement, the issue of shares in the Company is under the control of the directors.
    
    \item Subject to the Act and the Shareholders Agreement (including Reserved Matters requiring unanimous founder approval), the directors may issue shares to persons at times and on terms and conditions and having attached to them preferred, deferred or other special rights or restrictions as the directors see fit.
    
    \item Subject to the Act and the Shareholders Agreement, any preference shares may, with the sanction of a resolution of the Company in general meeting, be issued on the terms that they are, or at the option of the Company are, liable to be redeemed.
    
    \item The directors may grant to any person (including any directors, officer or employee of the Company or a related body corporate of the Company) options or other securities with rights of conversion to shares or preemptive rights to any shares for any consideration and for any period, subject to the Shareholders Agreement and applicable Reserved Matters.
    
    \item Any issue of new shares must comply with the pre-emptive rights, Reserved Matters, and other provisions set out in the Shareholders Agreement.
\end{enumerate}

\subsection{Pre-emption for existing members on issue of shares}

\begin{enumerate}[label=(\alph*)]
    \item Subject to the Shareholders Agreement, before issuing shares of a particular class, the directors must offer them to members holding shares of that class in accordance with the pre-emptive rights provisions set out in the Shareholders Agreement.
    
    \item For Additional Funding via the issue of new shares, the Company must first offer such shares to all existing shareholders pro rata to their existing percentage shareholdings as a Rights Offer in accordance with the Shareholders Agreement.
    
    \item The specific pre-emption procedures, including notice periods, acceptance procedures, and the order of offers, shall be as set out in the Shareholders Agreement.
    
    \item Any shares not taken up under the pre-emptive rights may be issued to third parties only with the approval required under the Shareholders Agreement and subject to any Reserved Matters.
    
    \item The members, by resolution in general meeting, may authorise the directors to make a particular issue of shares without complying with the pre-emptive rights provisions, provided such resolution is consistent with the Shareholders Agreement.
\end{enumerate} 