\section{Calls on partly paid shares}

\begin{enumerate}[label=(\alph*)]
    \item If shares in the Company are partly paid, the member is liable to pay calls on the shares in accordance with the terms on which the shares are on issue.
    
    \item A call may be made payable by instalments.
    
    \item A call may be revoked, postponed or extended as the directors determine.
    
    \item A call must be treated as made at the time when the resolution of the directors authorising the call is passed.
    
    \item Each member must pay the amount called on the member's shares according to the terms of the notice of call.
    
    \item At least 30 Business Days before the due date for payment, the Company must send notices to all members on whom the call is made who are on the Register when the call is announced. The notice must include each of the following:
    \begin{enumerate}[label=(\roman*)]
        \item the name of the member;
        \item the number of shares held by the member;
        \item the amount of the call;
        \item the due date for payment of the call; and
        \item the consequences of nonpayment of the call.
    \end{enumerate}
    
    \item The non receipt of a notice of a call by, or the accidental omission to give notice of a call to, any of the members does not invalidate the call.
    
    \item On the trial or hearing of any action for the recovery of any money due for any call and in any circumstances where it is necessary to prove the right to forfeit or sell shares for nonpayment of a call it is sufficient to prove:
    \begin{enumerate}[label=(\roman*)]
        \item that the name of the member sued is entered in the Register as the holder or one of the holders of the shares in respect of which the call was made;
        \item that the resolution making the call is recorded in the minute book;
        \item that:
        \begin{enumerate}[label=(\alph*)]
            \item notice of the call was given to the registered holder of the shares in accordance with this constitution; or
            \item in the case of calls or instalments payable at fixed times by the terms of issue of any share or otherwise, those terms apply; and
            \item that the sum or call has not been paid.
        \end{enumerate}
        \item Proof of the above matters is conclusive evidence of the debt and of the right to forfeit or sell shares for nonpayment of a call and it is not necessary to prove the appointment of the directors who made the call or the passing of the resolution or anything else.
    \end{enumerate}
    
    \item The joint holders of a share are jointly and severally liable to pay all calls in respect of the share.
    
    \item If a sum called is not paid on or before the date for payment, the person from whom the sum is due must pay interest on the sum (or on so much as remains unpaid) at the rate the directors determine calculated from the day payment is due till the time of actual payment. The directors may waive payment of that interest wholly or in part.
    
    \item Any sum that, by the terms of issue of a share, becomes payable on issue or at a fixed date, must be treated for the purposes of this constitution as a call duly made and payable on the date on which by the terms of issue the sum becomes payable. In case of nonpayment, the provisions of this constitution as to payment of interest and expenses, forfeiture or otherwise apply as if the sum had become payable by virtue of a call duly made and notified.
    
    \item The directors may, on the issue of shares, differentiate between the holders as to the amount of calls to be paid and the times of payment.
    
    \item The directors may accept from a member the whole or a part of the amount unpaid on a share although no part of that amount has been called up. The directors may authorise payment by the Company of interest upon the whole or any part of an amount so accepted, until the amount becomes payable, at the rate agreed upon between the directors and the member paying the sum.
    
    \item Any amount paid in advance of calls is not included or taken into account in ascertaining the amount of dividend payable upon the shares in respect of which the advance has been made.
    
    \item The directors may at any time repay the amount so advanced upon giving to such member one month's notice in writing.
    
    \item If a sum called in respect of a share is not paid before or on the due date for payment, the Company may recover the sum as a debt due with interest and expenses (if any), by action or otherwise but the exercise of this right is without prejudice to the right to forfeit the share of the member in arrears, and the directors may exercise either or both of these rights in their discretion.
\end{enumerate} 