\section{Shareholders Agreement compliance}

\subsection{Primacy of Shareholders Agreement}

\begin{enumerate}[label=(\alph*)]
    \item Where there is any inconsistency between the provisions of this constitution and the Shareholders Agreement, the provisions of the Shareholders Agreement shall prevail to the extent of the inconsistency.
    
    \item All share transfers, share issues, corporate governance matters, and other matters covered by both this constitution and the Shareholders Agreement shall be conducted in accordance with the Shareholders Agreement.
    
    \item The directors and members acknowledge that certain matters are designated as "Reserved Matters" under the Shareholders Agreement and require unanimous founder approval, notwithstanding any broader powers that may be conferred by this constitution.
\end{enumerate}

\subsection{Share transfer restrictions}

\begin{enumerate}[label=(\alph*)]
    \item No transfer of shares shall be registered by the Company unless it complies with the transfer restrictions and procedures set out in the Shareholders Agreement.
    
    \item The Company shall not recognize any purported transfer of shares that does not comply with the Shareholders Agreement, regardless of whether such transfer might otherwise be permitted under this constitution.
    
    \item All share transfers are subject to the specific restrictions applicable to each share class as set out in the Shareholders Agreement, including but not limited to:
    \begin{enumerate}[label=(\roman*)]
        \item Lock-up periods for Ordinary Shares (Voting);
        \item Right of first refusal procedures for Preference Shares (Non-Voting);
        \item Employment-based restrictions for Employee Ordinary Shares (Non-Voting).
    \end{enumerate}
\end{enumerate}

\subsection{Corporate governance}

\begin{enumerate}[label=(\alph*)]
    \item The composition, powers, and procedures of the board of directors shall be as set out in the Shareholders Agreement.
    
    \item All Reserved Matters as defined in the Shareholders Agreement require the approval specified therein, notwithstanding any other provision of this constitution.
    
    \item The information rights, board observer rights, and other governance rights of shareholders shall be as set out in the Shareholders Agreement.
\end{enumerate} 