\section{Technology meeting of directors}

\begin{enumerate}[label=(\alph*)]
    \item A directors' meeting may be held using telephone or, if consented to by all directors, other technology. The consent may be a standing one. A director may only withdraw the consent within a reasonable period before the meeting.
    
    \item If a directors' meeting is held using any technology and all the directors take part in the meeting, they must be treated as having consented to the use of the technology for that meeting.
    
    \item The following provisions apply to a technology meeting:
    \begin{enumerate}[label=(\roman*)]
        \item each of the directors taking part in the meeting must be able to hear and be heard by each of the other directors taking part in the meeting; and
        \item at the commencement of the meeting each director must announce his or her presence to all the other directors taking part in the meeting.
    \end{enumerate}
    
    \item If the secretary is not present at a technology meeting or the Company does not have a secretary one of the directors present or another person nominated by them present at the meeting must take minutes of the meeting.
    
    \item A director may not leave a technology meeting by disconnecting his or her link to the meeting unless that director has previously notified the chairperson of the meeting.
    
    \item A director is conclusively presumed to have been present and to have formed part of a quorum at all times during a technology meeting unless that director has previously obtained the express consent of the chairperson to leave the meeting.
\end{enumerate} 