\section{Sale of shares subject to lien}

\begin{enumerate}[label=(\alph*)]
    \item Subject to rule 11.b, the Company may sell, in the manner the directors see fit, any shares on which the Company has a lien.
    
    \item The Company must not sell a share on which it has a lien unless:
    \begin{enumerate}[label=(\roman*)]
        \item a sum in respect of which the lien exists is presently payable; and
        \item the Company has, not less than 14 days before the date of the sale, given to the registered holder for the time being of the share or the person entitled to the share by reason of the death or bankruptcy of the registered holder a notice in writing setting out, and demanding payment of, the sum presently payable in respect of which the lien exists.
    \end{enumerate}
    
    \item To give effect to a sale of shares under rule 11, the directors may authorise a person to transfer the shares sold to the purchaser of the shares.
    
    \item The Company must register the purchaser as the holder of the shares comprised in the transfer and the purchaser is not bound to see to the application of the purchase money.
    
    \item The title of the purchaser to the shares is not affected by any irregularity or invalidity in connection with the sale.
    
    \item The proceeds of a sale under rule 11 must be applied by the Company as follows:
    \begin{enumerate}[label=(\roman*)]
        \item in payment of the sum presently payable in respect of which the lien existed;
        \item if there was a lien on the shares for sums not presently payable, the Company may retain any residue of the proceeds of sale and apply the residue to pay those sums when they become presently payable;
        \item subject to rule 11.f.ii, the Company must pay the residue to the person entitled to the shares immediately before the sale.
    \end{enumerate}
\end{enumerate}

\textbf{Note:} Any sale of shares under this section is subject to the transfer restrictions and procedures set out in the Shareholders Agreement. The Company must ensure that any sale complies with the specific restrictions applicable to each share class, including lock-up periods, rights of first refusal, and other transfer limitations. 