\section{Quorum for meeting of members}

\begin{enumerate}[label=(\alph*)]
    \item The quorum for a meeting of the Company's members consists of:
    \begin{enumerate}[label=(\roman*)]
        \item where the number of members with voting rights is two or more, at least two (2) shareholders present in person or by proxy, holding between them at least seventy-five percent (75\%) of the total issued Ordinary Shares (Voting); or
        \item where only one member has voting rights, that member.
    \end{enumerate}
    
    The quorum must be present at all times during the meeting.
    
    \item In determining whether a quorum is present, individuals attending as proxies, attorneys or body corporate representatives are counted. However, if a member has appointed more than one proxy, attorney or representative, only one of them is counted. If an individual is attending both as a member and as a proxy, attorney or body corporate representative, the individual is counted only once.
    
    \item If a quorum is not present at a meeting of the Company's members, the meeting is automatically deemed to have been adjourned and the adjourned meeting will be held at the same time and the same place on the day after such meeting.
    
    \item If no quorum is present at the general meeting adjourned under rule 40.c within 30 minutes after the time for the general meeting, the directors may, in their absolute discretion, declare the meeting dissolved or deem that those members present in person form a quorum and may transact the business for which the meeting was called.
\end{enumerate}

\textbf{Note:} This quorum requirement aligns with the Shareholders Agreement provision requiring at least 75\% of voting shares for shareholder meetings. Only holders of Ordinary Shares (Voting) are counted for quorum purposes, consistent with the share class structure. 