\section{FUTURE FUNDING AND SHARE ALLOCATION}

\subsection{Share Class Structure and Allocation}
\begin{enumerate}[label=(\alph*)]
\item The Company has authorized three classes of shares:
    \begin{enumerate}[label=(\roman*)]
    \item Ordinary Shares (Voting): 10,000,000 shares (84\%) - Founders only;
    \item Preference Shares (Non-Voting): 1,190,476 shares (10\%) - Strategic investors;
    \item Employee Ordinary Shares (Non-Voting): 714,286 shares (6\%) - Employees and advisors.
    \end{enumerate}
\item All share issuances from reserved pools require unanimous Board approval.
\item Founders maintain 100\% voting control through Ordinary Shares (Voting).
\item Non-voting shareholders receive economic participation without governance rights.
\end{enumerate}

\subsection{Strategic Investor Participation}
\begin{enumerate}[label=(\alph*)]
\item Strategic investors receive Preference Shares (Non-Voting) with the following rights:
    \begin{enumerate}[label=(\roman*)]
    \item Cumulative 8\% preference dividend (if declared);
    \item 1x non-participating liquidation preference;
    \item Weighted average broad-based anti-dilution protection;
    \item Monthly management accounts and annual audited accounts;
    \item Right to appoint one non-voting board observer;
    \item Tag-along and drag-along participation rights;
    \item Optional conversion to Ordinary Shares (Voting).
    \end{enumerate}
\item Minimum investment threshold: AUD \$100,000 per investor.
\item Maximum allocation: 1,190,476 Preference Shares (10\% of total authorized).
\item Strategic investors must execute a Deed of Accession to this Agreement.
\end{enumerate}

\subsection{Employee Share Plan}
\begin{enumerate}[label=(\alph*)]
\item Employees receive Employee Ordinary Shares (Non-Voting) with the following characteristics:
    \begin{enumerate}[label=(\roman*)]
    \item Pro-rata dividend rights after preference dividends;
    \item Pro-rata liquidation rights after preference liquidation;
    \item Subject to employment-based vesting schedules;
    \item Company right of first refusal on transfers;
    \item Eligible for Australian ESS tax concessions;
    \item No voting rights or governance participation.
    \end{enumerate}
\item Standard vesting schedule: 12-month cliff, 36-month total vesting.
\item Maximum allocation: 714,286 Employee Ordinary Shares (6\% of total authorized).
\item Employee allocations require:
    \begin{enumerate}[label=(\roman*)]
    \item Unanimous Board approval;
    \item Execution of Employee Share Plan Agreement;
    \item Compliance with ESS tax regulations;
    \item Independent valuation for tax purposes.
    \end{enumerate}
\end{enumerate}

\subsection{Advisor and Consultant Allocation}
\begin{enumerate}[label=(\alph*)]
\item Advisors may receive Employee Ordinary Shares (Non-Voting) from the employee pool.
\item Typical advisor allocation: 0.1\% to 1\% depending on contribution and stage.
\item Advisor vesting: 12-24 month vesting period with quarterly vesting.
\item Advisory agreements must specify:
    \begin{enumerate}[label=(\roman*)]
    \item Scope of advisory services;
    \item Time commitment expectations;
    \item Confidentiality obligations;
    \item Share allocation and vesting terms.
    \end{enumerate}
\end{enumerate}

\subsection{Additional Capital Requirements}
\begin{enumerate}[label=(\alph*)]
\item If the Company requires capital beyond reserved share pools, it shall:
    \begin{enumerate}[label=(\roman*)]
    \item First offer existing Ordinary Shareholders pro-rata rights;
    \item Issue new shares at fair market value determined by independent valuation;
    \item Provide 30 Business Days for existing shareholders to accept;
    \item Offer unsubscribed shares to third parties on no more favorable terms.
    \end{enumerate}
\item New share issuances may create additional share classes if required.
\item Founders maintain the right to approve all new share issuances.
\end{enumerate}

\subsection{Anti-Dilution and Pre-Emptive Rights}
\begin{enumerate}[label=(\alph*)]
\item Ordinary Shareholders (Voting) maintain pre-emptive rights on all new issuances.
\item Preference Shareholders receive weighted average broad-based anti-dilution protection.
\item Employee Ordinary Shareholders have no pre-emptive or anti-dilution rights.
\item Anti-dilution protection excludes:
    \begin{enumerate}[label=(\roman*)]
    \item Employee share plan issuances;
    \item Share splits or stock dividends;
    \item Conversion of existing securities;
    \item Strategic partnership issuances approved by Board.
    \end{enumerate}
\end{enumerate}

\subsection{Valuation and Pricing}
\begin{enumerate}[label=(\alph*)]
\item All share issuances must be at fair market value determined by:
    \begin{enumerate}[label=(\roman*)]
    \item Independent professional valuation; or
    \item Board-approved methodology using comparable company analysis; or
    \item Recent arm's length transaction pricing.
    \end{enumerate}
\item Employee shares may be issued at discount for ESS tax benefit purposes.
\item Preference shares may include liquidation preference in pricing calculations.
\item Valuation methodology must be consistent across share classes.
\end{enumerate}

\subsection{R\&D and Growth Funding}
\begin{enumerate}[label=(\alph*)]
\item The Company shall maintain adequate funding for:
    \begin{enumerate}[label=(\roman*)]
    \item AI technology research and development;
    \item Voice synthesis and natural language processing improvements;
    \item Algorithm optimization and machine learning infrastructure;
    \item Platform scaling and security enhancements;
    \item Talent acquisition and retention.
    \end{enumerate}
\item R\&D funding decisions require Board approval.
\item The Company shall pursue available R\&D tax incentives and government grants.
\item Funding priorities align with Company's AI voice agent technology focus.
\end{enumerate}

\subsection{External Investment}
\begin{enumerate}[label=(\alph*)]
\item The Company may seek external investment with approval of 75\% of Shareholders.
\item External investment terms must ensure:
    \begin{enumerate}[label=(\roman*)]
    \item protection of existing Shareholders' rights;
    \item maintenance of Board control;
    \item protection of intellectual property;
    \item appropriate valuation of the Company;
    \item compliance with AI industry standards and regulations.
    \end{enumerate}
\end{enumerate}

\subsection{Shareholder Loans}
\begin{enumerate}[label=(\alph*)]
\item Shareholders may provide loans to the Company on terms approved by the Board.
\item Loans must be:
    \begin{enumerate}[label=(\roman*)]
    \item documented in writing;
    \item on arms-length terms;
    \item subordinate to external finance;
    \item convertible to equity at the Company's option;
    \item secured appropriately if required.
    \end{enumerate}
\end{enumerate} 