\section{INTELLECTUAL PROPERTY AND CONFIDENTIALITY}

\subsection{Current IP Ownership}
\begin{enumerate}[label=(\alph*)]
\item All Intellectual Property Rights related to The Augmented 4 Pty Ltd's technology, including but not limited to AI voice agent technologies, algorithms, source code, models, and associated intellectual property (the ``Company IP'') are currently owned exclusively by Domenico Rutigliano.

\item The Company acknowledges and agrees that Domenico Rutigliano is the sole and exclusive owner of all Company IP as of the date of this Agreement.

\item The Company and other Shareholders acknowledge that this ownership arrangement is integral to the Company's initial structure and valuation.

\item This IP ownership structure is separate from and does not affect the share class structure or voting rights under this Agreement.
\end{enumerate}

\subsection{Future IP Assignment}
\begin{enumerate}[label=(\alph*)]
\item Upon the occurrence of a Capital Raise Event (as defined below), Domenico Rutigliano agrees to assign all Company IP to The Augmented 4 Pty Ltd.

\item For the purposes of this section, a ``Capital Raise Event'' means any:
    \begin{enumerate}[label=(\roman*)]
    \item equity investment into the Company by a third party from the Preference Share pool of at least AUD 750,000 in a single transaction or series of related transactions within a 12-month period;
    \item initial public offering of the Company's shares; or
    \item other capital raising event of at least AUD 750,000 as unanimously agreed by the Ordinary Shareholders (Voting).
    \end{enumerate}

\item In consideration for the assignment of Company IP, the Company shall pay to Domenico Rutigliano:
    \begin{enumerate}[label=(\roman*)]
    \item a one-time payment of AUD 100,000; and
    \item any applicable taxes associated with the assignment.
    \end{enumerate}

\item \textbf{Personal Loan Repayment Obligation:} Upon receipt of the AUD 100,000 IP compensation payment, Domenico Rutigliano shall immediately repay in full all personal loans provided by Michael Scheelhardt to Domenico Rutigliano as documented in Schedule 6 (Personal Loan Register) to this Agreement. The parties acknowledge that these personal loans are separate from and independent of this Shareholders Agreement, but the repayment obligation is incorporated herein for commercial certainty and enforceability.

\item Alternative Revenue-Based Compensation:
    \begin{enumerate}[label=(\roman*)]
    \item If the Capital Raise Event does not generate sufficient funds to pay the AUD 100,000 compensation, the Company shall pay Domenico Rutigliano through a revenue-sharing arrangement.
    \item The percentage of revenue to be allocated shall be determined by unanimous Board approval (requiring both founders' consent).
    \item This revenue-sharing arrangement shall continue until the full AUD 100,000 compensation has been paid.
    \item Upon reaching the total compensation of AUD 100,000, Domenico Rutigliano shall execute the IP Assignment Deed.
    \item The Board shall review and adjust the revenue-sharing percentage quarterly to ensure both Company sustainability and timely compensation, subject to unanimous founder approval.
    \item \textbf{Personal Loan Repayment under Revenue-Sharing:} If IP compensation is paid through revenue-sharing, Domenico Rutigliano shall repay all personal loans from Michael Scheelhardt (as documented in Schedule 6) through monthly interest-free installments. The monthly repayment amount shall be proportional to the monthly IP compensation received, ensuring full repayment is completed simultaneously with the completion of the AUD 100,000 IP compensation payment.
    \end{enumerate}

\item The assignment shall be documented in a formal IP Assignment Deed, which shall:
    \begin{enumerate}[label=(\roman*)]
    \item be executed within 30 days of either:
        \begin{enumerate}[label=(a)]
        \item the Capital Raise Event; or
        \item the completion of the AUD 100,000 payment through revenue sharing;
        \end{enumerate}
    \item include comprehensive schedules of all assigned IP;
    \item contain customary warranties and indemnities; and
    \item be in a form reasonably satisfactory to both founders.
    \end{enumerate}

\item IP assignment decisions require unanimous approval of Ordinary Shareholders (Voting) as a Reserved Matter.
\end{enumerate}

\subsection{Interim IP License}
\begin{enumerate}[label=(\alph*)]
\item Until the occurrence of a Capital Raise Event, Domenico Rutigliano grants to the Company an exclusive, worldwide, royalty-free license to use, modify, and commercialize the Company IP for the purposes of conducting the Business.

\item This license shall:
    \begin{enumerate}[label=(\roman*)]
    \item be irrevocable except in the case of material breach by the Company;
    \item include the right to sublicense with unanimous Board approval (both founders' consent);
    \item terminate automatically upon the assignment of Company IP to the Company; and
    \item survive the termination of this Agreement until the IP assignment occurs.
    \end{enumerate}

\item Sublicensing rights and material IP licensing decisions require unanimous approval of Ordinary Shareholders (Voting).
\end{enumerate}

\subsection{Technology Protection and Governance}
\begin{enumerate}[label=(\alph*)]
\item The Company shall maintain:
    \begin{enumerate}[label=(\roman*)]
    \item Comprehensive IP registration and protection strategy;
    \item Regular IP audits and reviews;
    \item Secure source code repositories;
    \item AI model version control and security;
    \item Data protection and privacy compliance systems;
    \item Technical documentation of all IP assets.
    \end{enumerate}

\item All material IP protection decisions require unanimous Board approval.

\item IP strategy and protection measures shall be reported to all Ordinary Shareholders (Voting) quarterly.

\item Preference Shareholders (Non-Voting) receive information rights regarding IP protection but no decision-making authority.

\item Employee Ordinary Shareholders (Non-Voting) have no IP governance rights but benefit from IP value through their economic participation.
\end{enumerate}

\subsection{Employee IP Contributions}
\begin{enumerate}[label=(\alph*)]
\item All IP created by employees in the course of their employment automatically belongs to the Company upon IP assignment completion.

\item Prior to IP assignment, employee IP contributions are licensed to the Company under the same terms as the interim license.

\item Employee IP assignment agreements shall include:
    \begin{enumerate}[label=(\roman*)]
    \item Assignment of all work-related IP to the Company;
    \item Moral rights waivers where applicable;
    \item Confidentiality and non-disclosure obligations;
    \item Post-employment IP restrictions.
    \end{enumerate}

\item Employee IP contributions do not affect their Employee Ordinary Share (Non-Voting) allocations or vesting schedules.
\end{enumerate}

\subsection{Confidentiality Obligations by Share Class}
\begin{enumerate}[label=(\alph*)]
\item \textbf{All Shareholders} must maintain strict confidentiality of:
    \begin{enumerate}[label=(\roman*)]
    \item All Company IP and technical information;
    \item Business strategies and commercial information;
    \item Customer data and relationships;
    \item Financial information and performance data;
    \item This Agreement and its terms.
    \end{enumerate}

\item \textbf{Ordinary Shareholders (Voting)} have access to all confidential information necessary for governance decisions.

\item \textbf{Preference Shareholders (Non-Voting)} receive confidential information subject to their information rights and investment protection needs.

\item \textbf{Employee Ordinary Shareholders (Non-Voting)} receive confidential information necessary for their employment duties and share participation.

\item Confidentiality obligations:
    \begin{enumerate}[label=(\roman*)]
    \item Survive termination of this Agreement indefinitely;
    \item Apply to all representatives and advisors;
    \item Include return/destruction of confidential materials upon request;
    \item Require immediate reporting of unauthorized disclosures.
    \end{enumerate}

\item Breach of confidentiality may result in forfeiture of unvested Employee Ordinary Shares (Non-Voting) and other remedies available at law or equity.
\end{enumerate}

\subsection{Tax Treatment and Compliance}
\begin{enumerate}[label=(\alph*)]
\item \textbf{Tax Treatment Disclaimer:} Each party acknowledges that the Company does not provide tax advice, and the parties shall obtain their own independent tax advice regarding the IP compensation and related transactions. Nothing in this Agreement shall be construed as a representation or warranty regarding the tax treatment of any payment, assignment, or transfer. All taxes (including income tax, GST, or capital gains tax, if any) arising from or in connection with the IP compensation shall be the sole responsibility of the recipient, unless otherwise agreed in writing.
\end{enumerate}