\section{SHARE TRANSFER RESTRICTIONS}

\subsection{Lock-up Period}
\begin{enumerate}[label=(\alph*)]
\item During the Lock-up Period, no Shareholder shall Transfer any Shares except:
    \begin{enumerate}[label=(\roman*)]
    \item with unanimous written consent of all other Shareholders;
    \item pursuant to an Exit Event approved under clause 8;
    \item to a Permitted Transferee as defined in clause 7.2.
    \end{enumerate}
\item Any purported Transfer in breach of this clause is void.
\end{enumerate}

\subsection{Right of First Refusal}
\begin{enumerate}[label=(\alph*)]
\item After the Lock-up Period, any Shareholder (``Selling Shareholder'') who wishes to Transfer any Shares must first offer them to the other Shareholders pro rata to their existing shareholdings.
\item The offer must be in writing (``Transfer Notice'') and specify:
    \begin{enumerate}[label=(\roman*)]
    \item number and class of Shares offered;
    \item price per Share;
    \item payment terms;
    \item identity of proposed transferee.
    \end{enumerate}
\item Other Shareholders have 30 Business Days to accept the offer.
\item If not all Shares are acquired by other Shareholders, the Selling Shareholder may Transfer remaining Shares to the proposed transferee within 90 days at a price not less than specified in the Transfer Notice.
\end{enumerate}

\subsection{Tag-Along Rights}
\begin{enumerate}[label=(\alph*)]
\item If a Shareholder proposes to Transfer 50\% or more of the total issued Shares, other Shareholders may participate in the sale pro rata (``Tag-Along Right'').
\item The selling Shareholder must give 30 days' notice of the proposed sale (``Tag-Along Notice'').
\item Other Shareholders may exercise Tag-Along Rights by written notice within 20 Business Days.
\item All Shares will be sold on identical terms and conditions.
\end{enumerate}

\subsection{Drag-Along Rights}
\begin{enumerate}[label=(\alph*)]
\item If Shareholders holding 75\% or more of Shares (``Majority Shareholders'') wish to Transfer all their Shares, they may require other Shareholders to sell all their Shares to the same purchaser.
\item Majority Shareholders must give 30 days' notice (``Drag-Along Notice'').
\item The sale price and terms must be the same for all Shares.
\item All Shareholders must cooperate to effect the sale including executing all required documents.
\end{enumerate} 