\section{Transfer of Shares}

\subsection{General Prohibition and Share Class Transfer Restrictions}
\begin{enumerate}[label=(\alph*)]
\item No Shareholder may Transfer any Shares, whether directly or indirectly, except as expressly permitted by this Agreement and subject to the specific restrictions applicable to each share class.
\item \textbf{Ordinary Shares (Voting) - Founder Lock-up:} During the Lock-up Period (being a period of five (3) years from the Effective Date), holders of Ordinary Shares (Voting) shall not Transfer any such Shares except:
    \begin{enumerate}[label=(\roman*)]
    \item with the prior unanimous written consent of all Ordinary Shareholders (Voting);
    \item pursuant to the provisions of the Exit Events clause of this Agreement;
    \item to a Permitted Transferee in accordance with subsection \ref{subsec:PermittedTransfers} below.
    \end{enumerate}
\item \textbf{Preference Shares (Non-Voting) - Investor Transfers:} Preference Shares (Non-Voting) may be transferred subject to:
    \begin{enumerate}[label=(\roman*)]
    \item Right of first refusal to Ordinary Shareholders (Voting);
    \item Board approval (unanimous founder consent);
    \item Transferee execution of Deed of Accession;
    \item Compliance with tag-along and drag-along provisions.
    \end{enumerate}
\item \textbf{Employee Ordinary Shares (Non-Voting) - Employment Restrictions:} Employee Ordinary Shares (Non-Voting) are subject to:
    \begin{enumerate}[label=(\roman*)]
    \item Vesting schedules and forfeiture provisions;
    \item Company right of first refusal;
    \item Transfer restrictions during employment and for 12 months post-termination;
    \item Board approval for any transfers.
    \end{enumerate}
\item Any purported Transfer of Shares not made in strict accordance with this Agreement shall be void and of no effect, and the Company shall not recognise or register any such Transfer.
\end{enumerate}

\subsection{Permitted Transfers by Share Class} \label{subsec:PermittedTransfers}
\begin{enumerate}[label=(\alph*)]
\item \textbf{Ordinary Shares (Voting):} Founders may transfer to Permitted Transferees including:
    \begin{enumerate}[label=(\roman*)]
    \item Immediate family members;
    \item Family trusts where founder is beneficiary;
    \item Wholly-owned corporate entities;
    \item Transfers pursuant to estate planning or succession.
    \end{enumerate}
\item \textbf{Preference Shares (Non-Voting):} Investors may transfer to:
    \begin{enumerate}[label=(\roman*)]
    \item Affiliated investment funds or entities;
    \item Other institutional investors approved by Board;
    \item Transfers pursuant to fund liquidation or succession.
    \end{enumerate}
\item \textbf{Employee Ordinary Shares (Non-Voting):} Employees may transfer only:
    \begin{enumerate}[label=(\roman*)]
    \item Vested shares to immediate family members;
    \item Pursuant to estate planning with Company approval;
    \item Back to Company under buyback provisions.
    \end{enumerate}
\item No Transfer to a Permitted Transferee shall be effective until the Permitted Transferee has executed a Deed of Accession in accordance with subsection \ref{subsec:DeedOfAccession}.
\end{enumerate}

\subsection{Right of First Refusal by Share Class} \label{subsec:ROFR}
\begin{enumerate}[label=(\alph*)]
\item \textbf{Ordinary Shares (Voting) ROFR:} Any proposed transfer of Ordinary Shares (Voting) must first be offered to:
    \begin{enumerate}[label=(\roman*)]
    \item The other Ordinary Shareholder (Voting) with full right of first refusal;
    \item If declined, to the Company for buyback;
    \item If declined, subject to Board approval for third-party transfer.
    \end{enumerate}
\item \textbf{Preference Shares (Non-Voting) ROFR:} Any proposed transfer must be offered to:
    \begin{enumerate}[label=(\roman*)]
    \item Other Preference Shareholders pro-rata to their holdings;
    \item Ordinary Shareholders (Voting) if declined by Preference Shareholders;
    \item Third parties with Board approval if declined by all shareholders.
    \end{enumerate}
\item \textbf{Employee Ordinary Shares (Non-Voting) ROFR:} Any proposed transfer must be offered to:
    \begin{enumerate}[label=(\roman*)]
    \item The Company at fair market value;
    \item Other employees participating in the share plan;
    \item Ordinary Shareholders (Voting) if declined by Company and employees.
    \end{enumerate}
\item ROFR procedures require 30 Business Days notice and acceptance period.
\item Valuation for ROFR purposes shall be determined by independent valuation or Board-approved methodology.
\end{enumerate}

\subsection{Tag-Along Rights by Share Class} \label{subsec:TagAlong}
\begin{enumerate}[label=(\alph*)]
\item \textbf{Founder Share Transfers:} If Ordinary Shareholders (Voting) propose to transfer shares representing 25\% or more of voting control, all other shareholders have tag-along rights:
    \begin{enumerate}[label=(\roman*)]
    \item Other Ordinary Shareholders (Voting): Full pro-rata tag-along rights;
    \item Preference Shareholders (Non-Voting): Tag-along rights based on liquidation preference;
    \item Employee Ordinary Shareholders (Non-Voting): Tag-along rights for vested shares only.
    \end{enumerate}
\item \textbf{Investor Share Transfers:} If Preference Shareholders propose to transfer 50\% or more of their holdings:
    \begin{enumerate}[label=(\roman*)]
    \item Other Preference Shareholders have pro-rata tag-along rights;
    \item Ordinary Shareholders (Voting) have tag-along rights at their discretion;
    \item Employee Ordinary Shareholders have no tag-along rights.
    \end{enumerate}
\item Tag-along procedures require 30 Business Days notice and 20 Business Days exercise period.
\item All tag-along participants receive same price per share adjusted for share class rights.
\end{enumerate}

\subsection{Drag-Along Rights} \label{subsec:DragAlong}
\begin{enumerate}[label=(\alph*)]
\item \textbf{Founder Drag-Along Authority:} Ordinary Shareholders (Voting) holding 75\% or more of voting shares may exercise drag-along rights over all other shareholders.
\item \textbf{Enhanced Protections for Non-Voting Shareholders:}
    \begin{enumerate}[label=(\roman*)]
    \item Independent valuation required confirming fair market value;
    \item Preference Shareholders receive liquidation preference protection;
    \item Employee Ordinary Shareholders receive acceleration of vesting for unvested shares;
    \item All shareholders receive same economic treatment adjusted for share class rights.
    \end{enumerate}
\item \textbf{Board Approval Requirement:} Drag-along requires unanimous Board approval (both founders) confirming:
    \begin{enumerate}[label=(\roman*)]
    \item Transaction is in Company's best interests;
    \item Fair value provided to all shareholders;
    \item Proper protection for minority shareholders.
    \end{enumerate}
\item \textbf{Legal and Regulatory Compliance:}
    \begin{enumerate}[label=(\roman*)]
    \item The Drag-Along Sale must comply with all applicable laws, including the Corporations Act 2001 (Cth).
    \item Shareholders must receive all necessary disclosures and documentation.
    \item The transaction must not prejudice minority shareholders unfairly.
    \end{enumerate}
\item \textbf{Minimum Protection Period:} No drag-along may be exercised within 36 months of Effective Date except with unanimous shareholder consent.
\item Drag-along procedures require 30 Business Days notice and independent fairness opinion.
\item \textbf{Valuation Floor:}
    \begin{enumerate}[label=(\roman*)]
    \item The offer must meet a minimum valuation threshold agreed by the Board.
    \end{enumerate}
\end{enumerate}

\subsection{Employee Share Forfeiture and Buyback}
\begin{enumerate}[label=(\alph*)]
\item \textbf{Unvested Share Forfeiture:} Upon termination of employment:
    \begin{enumerate}[label=(\roman*)]
    \item All unvested Employee Ordinary Shares (Non-Voting) are forfeited to Company;
    \item Forfeiture occurs automatically without compensation;
    \item Good leaver vs. bad leaver provisions apply per employment agreements.
    \end{enumerate}
\item \textbf{Vested Share Buyback:} Company has option to repurchase vested Employee Ordinary Shares:
    \begin{enumerate}[label=(\roman*)]
    \item At fair market value determined by independent valuation;
    \item Exercise period of 90 days post-termination;
    \item Payment terms of 30 days cash or 12-month installments;
    \item Employee may retain shares if Company declines buyback option.
        \end{enumerate}
\item \textbf{Acceleration Provisions:} Vesting acceleration occurs upon:
    \begin{enumerate}[label=(\roman*)]
    \item Change of control (drag-along or sale of Company);
    \item Involuntary termination without cause;
    \item Death or permanent disability;
    \item Board-approved acceleration for retention purposes.
    \end{enumerate}
\end{enumerate}

\subsection{Deed of Accession by Share Class} \label{subsec:DeedOfAccession}
\begin{enumerate}[label=(\alph*)]
\item Any person acquiring Shares (whether by transfer from an existing Shareholder or by subscription for new Shares) must execute a Deed of Accession in the form set out in Annexure A before being registered as a Shareholder.
\item The Deed of Accession ensures that all new Shareholders are bound by the terms of this Agreement.
\item No Share transfer or new Share issue shall be registered until the relevant Deed of Accession has been executed.
\end{enumerate}

\subsection{Valuation Methodology for Transfers}
\begin{enumerate}[label=(\alph*)]
\item \textbf{Independent Valuation Required for:}
    \begin{enumerate}[label=(\roman*)]
    \item All drag-along transactions;
    \item Employee share buybacks;
    \item Disputes over ROFR pricing;
    \item Third-party transfers requiring Board approval.
    \end{enumerate}
\item \textbf{Valuation Methodology:}
    \begin{enumerate}[label=(\roman*)]
    \item Discounted cash flow analysis;
    \item Comparable company multiples;
    \item Recent transaction pricing;
    \item Asset-based valuation where appropriate.
    \end{enumerate}
\item \textbf{Share Class Adjustments:}
    \begin{enumerate}[label=(\roman*)]
    \item Preference Shares valued including liquidation preference;
    \item Employee Ordinary Shares valued on as-converted basis;
    \item Voting premium applied to Ordinary Shares (Voting) where appropriate.
    \end{enumerate}
\item Valuation costs borne by party requesting transfer unless otherwise specified.
\end{enumerate}

\subsection{No Encumbrances by Share Class}
\begin{enumerate}[label=(\alph*)]
\item \textbf{Ordinary Shares (Voting):} No encumbrances without unanimous founder consent.
\item \textbf{Preference Shares (Non-Voting):} Limited encumbrances permitted for:
    \begin{enumerate}[label=(\roman*)]
    \item Fund financing arrangements with Board approval;
    \item Institutional investor portfolio financing;
    \item Security interests approved by Board.
    \end{enumerate}
\item \textbf{Employee Ordinary Shares (Non-Voting):} No encumbrances permitted except:
    \begin{enumerate}[label=(\roman*)]
    \item Company security interests for loan arrangements;
    \item Court-ordered attachments;
    \item Tax liens with Company notification.
\end{enumerate}
\end{enumerate}

\subsection{Company's Obligation to Register Transfers}
\begin{enumerate}[label=(\alph*)]
\item Company shall register transfers complying with this Agreement and Constitution.
\item Board may refuse registration of non-compliant transfers.
\item Share class-specific transfer requirements must be satisfied.
\item Proper Deed of Accession required for all transfers.
\item Transfer register shall maintain separate records for each share class.
\end{enumerate}
% Add LaTeX labels to subsections for \ref{} if needed, e.g., \label{sec:transfer_of_shares} 