\section{MANAGEMENT AND GOVERNANCE}

\subsection{Board Composition}
\begin{enumerate}[label=(\alph*)]
\item The Board shall consist of two (2) directors initially comprising:
    \begin{enumerate}[label=(\roman*)]
    \item Domenico Rutigliano as Chief Technology Officer (CTO)
    \item Michael Scheelhardt as Chief Revenue Officer (CRO)
    \end{enumerate}
\item Each Shareholder has the right to appoint and maintain one director on the Board.
\item The removal of any director requires the approval of the appointing Shareholder.
\item Any vacancy on the Board shall be filled by the Shareholder entitled to make the appointment.
\end{enumerate}

\subsection{Board Meetings}
\begin{enumerate}[label=(\alph*)]
\item Board meetings shall be held at least quarterly, and more frequently as required for the effective management of the Business.
\item Notice period for meetings shall be at least 7 Business Days, unless waived by all directors.
\item Quorum requires presence (in person or by electronic means) of all directors.
\item Meetings may be held by telephone, video conference or other electronic means agreed by the directors.
\item Written resolutions signed by all directors are as valid as resolutions passed at a meeting.
\end{enumerate}

\subsection{Management Roles and Responsibilities}
\begin{enumerate}[label=(\alph*), wide, labelwidth=!, labelindent=0pt]
\item The day-to-day management of the Company's business shall be conducted by the key executives appointed by the Board, subject to the overall direction and supervision of the Board and the budget and business plan approved by the Board and, where applicable, the Shareholders.
\item The initial key executives and their primary areas of responsibility are:

\subsubsection*{Chief Technology Officer (CTO) - Initially Domenico Rutigliano}
    \begin{itemize}
    \item Overall technical strategy, vision, and direction of the Company.
    \item Leading the development, implementation, and maintenance of the Company's AI voice agent technology, algorithms, software, and platforms.
    \item Overseeing the technical infrastructure, including its scalability, performance, and security, and managing the Company's data assets.
    \item Driving research and development (R\&D) initiatives to ensure the Company maintains technological leadership and fosters innovation.
    \item Managing and developing the Company's Intellectual Property portfolio related to its technology, in conjunction with any IP policies set by the Board.
    \item Leading, mentoring, and developing the technical team, fostering a culture of engineering excellence, collaboration, and continuous improvement.
    \item Identifying, assessing, and managing technology-related risks and ensuring compliance with relevant technical standards, best practices, and regulations.
    \item Reporting to the Board on all material technological matters.
    \end{itemize}

\subsubsection*{Chief Revenue Officer (CRO) - Initially Michael Scheelhardt}
    \begin{itemize}
    \item Developing and executing the Company's overall commercial strategy, go-to-market plans, and business development initiatives.
    \item Leading all sales, marketing, customer acquisition, and customer success efforts.
    \item Building and maintaining strong, long-term relationships with key customers, strategic partners, and other industry stakeholders.
    \item Identifying, evaluating, and pursuing new market opportunities, strategic partnerships, and channels for growth.
    \item Driving revenue growth, managing commercial operations, including developing pricing strategies, and leading contract negotiations.
    \item Developing and managing the Company's brand identity, market positioning, and all related communications.
    \item Providing market intelligence, customer feedback, and competitive analysis to the Board and technical teams to inform product development and overall business strategy.
    \item Reporting to the Board on all material commercial matters.
    \end{itemize}
\item The specific duties and responsibilities of any executive officer may be further defined, varied, or supplemented by the Board from time to time. The Board may also appoint other officers (such as a Chief Executive Officer, Chief Financial Officer, etc.) as it deems necessary, and the appointment of such officers may be a Reserved Matter.
\end{enumerate}

\subsection{Growth Commitment and Resource Allocation}
\begin{enumerate}[label=(\alph*), wide, labelwidth=!, labelindent=0pt]
\item \textbf{Customer Growth Target:} The Shareholders hereby commit to supporting the growth of the Company's customer base to at least 300 active customers within twelve (12) months from the Effective Date.
\item \textbf{Shareholder Commitments:} To achieve this target, each Shareholder specifically commits to:
    \begin{enumerate}[label=(\roman*)]
    \item In the case of Domenico Rutigliano (CTO):
        \begin{itemize}
        \item Providing all necessary technical support and development resources to ensure the AI voice agent technology can scale to accommodate the target customer base;
        \item Leveraging AI technology to optimize product capabilities, performance, and reliability;
        \item Implementing appropriate technical infrastructure to support the projected growth;
        \item Prioritizing development of features that enhance customer acquisition and retention;
        \item Ensuring adequate technical support capacity for the growing customer base.
        \end{itemize}
    \item In the case of Michael Scheelhardt (CRO):
        \begin{itemize}
        \item Executing effective sales and marketing strategies to achieve the customer acquisition targets;
        \item Leveraging existing industry relationships and networks to accelerate customer acquisition;
        \item Establishing efficient customer onboarding and success processes;
        \item Developing strategic partnerships to expand market reach;
        \item Monitoring customer satisfaction and addressing issues to minimize churn.
        \end{itemize}
    \end{enumerate}
\item \textbf{Resource Allocation:} Both Shareholders agree to prioritize the allocation of the Company's financial and human resources toward achieving the customer growth target, including:
    \begin{enumerate}[label=(\roman*)]
    \item Hiring appropriate staff within the economic capacity of the Company to support both technical and commercial functions;
    \item Ensuring that the monthly budget allocations align with the customer growth objectives;
    \item Adjusting resource allocation promptly based on performance data and market feedback;
    \item Leveraging automation and AI technology where possible to maximize efficiency and scalability.
    \end{enumerate}
\item \textbf{Progress Tracking:} The Board shall track progress toward the customer growth target through:
    \begin{enumerate}[label=(\roman*)]
    \item Monthly reviews of customer acquisition metrics;
    \item Quarterly assessment of resource requirements and allocation;
    \item Identifying and addressing any impediments to achieving the growth target;
    \item Regular revision of strategies and tactics based on performance.
    \end{enumerate}
\item \textbf{Alignment with KPIs:} This growth commitment aligns with the KPIs set forth in Schedule 4 for the purposes of Performance Share transfers. The Shareholders acknowledge that their individual and collective efforts to fulfill this growth commitment directly support the achievement of those KPIs.
\end{enumerate}

\subsection{Reserved Matters (Requiring Shareholder Approval)}
\begin{enumerate}[label=(\alph*), wide, labelwidth=!, labelindent=0pt]
\item Notwithstanding any other provision of this Agreement or the Company's Constitution, the Company shall not, and the Directors shall procure that the Company shall not, undertake any of the matters listed in \textbf{Schedule 2 (Reserved Matters)} to this Agreement without the prior written approval of Shareholders holding at least [Specify Threshold, e.g., seventy-five percent (75\%)] of the total issued voting Shares, or such higher percentage (including unanimity) as may be specified for particular matters in Schedule 2 (the ``Requisite Shareholder Approval'').
\item If a specific approval threshold for a Reserved Matter is not specified in Schedule 2, then unanimous approval of all Shareholders shall be required.
\item The Shareholders agree that Schedule 2 may be reviewed and amended from time to time by unanimous agreement of all Shareholders.
\end{enumerate}


\subsection{Shareholder Meetings}
\begin{enumerate}[label=(\alph*), wide, labelwidth=!, labelindent=0pt]
\item \textbf{Annual General Meeting (AGM):} The Company shall hold an AGM if required by and in accordance with the Corporations Act 2001.
\item \textbf{Other Meetings:} Other general meetings of Shareholders may be convened by any Director, or by Shareholders in accordance with the Corporations Act 2001.
\item \textbf{Notice:} Notice of Shareholder meetings shall be given in accordance with the Company's Constitution and the Corporations Act 2001 (typically at least 21 days, or 28 days for resolutions requiring special notice, unless a shorter period is agreed by all Shareholders entitled to attend and vote).
\item \textbf{Quorum:} The quorum for a Shareholder meeting shall be at least two (2) Shareholders present in person or by proxy, holding between them at least [e.g., 75\%] of the total issued voting Shares. If one Shareholder holds this percentage, then that one Shareholder shall constitute a quorum. If a quorum is not present within thirty (30) minutes after the time appointed for the meeting, the meeting shall be adjourned as per the Corporations Act or the Constitution.
\item \textbf{Voting:} At any general meeting, resolutions shall be decided on a show of hands unless a poll is demanded (before or on the declaration of the result of the show of hands) by:
    \begin{enumerate}[label=(\roman*), wide, labelwidth=!, labelindent=0pt]
    \item the Chairperson of the meeting;
    \item at least one Shareholder present in person or by proxy;
    \item any Shareholder or Shareholders representing not less than 5\% of the total voting rights of all Shareholders having the right to vote at the meeting; or
    \item any Shareholder or Shareholders holding Shares on which an aggregate sum has been paid up equal to not less than 5\% of the total sum paid up on all Shares conferring that right.
    \end{enumerate}
    On a show of hands, each Shareholder present in person or by proxy has one vote. On a poll, each Shareholder present in person or by proxy has one vote for each Share they hold.
\item \textbf{Proxies:} Shareholders are entitled to appoint proxies in accordance with the Corporations Act 2001.
\item \textbf{Resolutions:} Resolutions of Shareholders will be passed as ordinary resolutions (simple majority of votes cast) or special resolutions (at least 75\% of votes cast) as required by this Agreement, the Constitution, or the Corporations Act 2001. Certain matters, particularly Reserved Matters, may require higher thresholds or unanimity as specified in this Agreement.
\item \textbf{Written Resolutions of Shareholders:} A resolution in writing signed by all Shareholders entitled to vote on that resolution is as valid and effectual as if it had been passed at a general meeting of Shareholders duly convened and held.
\end{enumerate}

\subsection{Information Rights}
\begin{enumerate}[label=(\alph*), wide, labelwidth=!, labelindent=0pt]
\item Each Shareholder is entitled to receive timely and accurate information concerning the business and affairs of the Company, including but not limited to:
    \begin{enumerate}[label=(\roman*), wide, labelwidth=!, labelindent=0pt]
    \item Monthly management accounts (including profit and loss statement, balance sheet, cash flow statement, and key performance indicators (KPIs) relevant to the Business, including the KPIs set out in Schedule 4) within [e.g., fifteen (15)] Business Days of the end of each month.
    \item Quarterly financial and operational performance reviews, including a comparison against the approved budget and business plan, and strategic updates, within [e.g., twenty (20)] Business Days of the end of each quarter.
    \item Annual audited financial statements (or unaudited if an audit is not required by law or agreement) within [e.g., ninety (90)] days of the end of each Financial Year.
    \item The proposed annual business plan and budget for the upcoming Financial Year, at least [e.g., thirty (30)] Business Days prior to the commencement of that Financial Year, for review and approval as a Reserved Matter.
    \item Prompt notification of any material business developments, including entry into or termination of significant contracts, commencement or settlement of material litigation or regulatory investigations, or any event that could reasonably be expected to have a material adverse effect on the Company.
    \end{enumerate}
\item All Shareholders and their duly authorised representatives (provided they agree to reasonable confidentiality undertakings if required by the Board) shall have reasonable access during normal business hours, and upon reasonable prior written notice to the Company, to inspect the books, records, and properties of the Company and to discuss the affairs, finances, and accounts of the Company with its Directors and officers.
\end{enumerate}

\subsection{Company Secretary}
\begin{enumerate}[label=(\alph*), wide, labelwidth=!, labelindent=0pt]
\item The Board may appoint a Company Secretary on such terms and conditions as the Board thinks fit. The Company Secretary may be one of the Directors.
\item The Company Secretary will be responsible for the statutory registers and records of the Company, attendance at and minuting of Board and Shareholder meetings (if required), and lodgement of necessary documents with ASIC and other regulatory bodies, and such other duties as the Board may determine.
\end{enumerate}

\subsection{Relationship with Constitution and Corporations Act}
\begin{enumerate}[label=(\alph*), wide, labelwidth=!, labelindent=0pt]
\item This Agreement supplements the Company's Constitution and the Corporations Act 2001. 
\item To the extent permitted by law, in the event of any conflict or inconsistency between the provisions of this Agreement and the provisions of the Company's Constitution concerning the matters agreed between the Shareholders hereunder, the provisions of this Agreement shall prevail as between the Shareholders.
\item The Shareholders undertake to exercise their respective rights and powers (including voting rights) to give full effect to the provisions of this Agreement and shall, as soon as reasonably practicable, take all steps necessary to amend the Company's Constitution to ensure it is consistent with the terms of this Agreement, to the extent that it is not already so consistent.
\item For the avoidance of doubt, this Agreement does not replace the replaceable rules in the Corporations Act 2001, except to the extent that specific provisions in this Agreement or the Company's Constitution modify or exclude them.
\end{enumerate} 